\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-24 paper.tex
typo

For a given network scenario $ \mathbf{z}$ (where one link failure occurs) in consideration, 
%let
%$f^{\mathbf{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \mathbf{z}}_k$, where 
%$T^ { \mathbf{z}}_k$ denote the set of surviving tunnels for the s-d pair $k$ under scenario $ \mathbf{z}$.
the ration of allocated bandwidth to a user's demanded bandwidth is \footnote{This is the same as equation (3), but we omit the superscript $\mathbf{z}$ of $R_{dk}^\mathbf{z}$.}

@@

If for every $k$, $R_{dk}$ is larger than its demand (i.e., $R_{dk} \ge 1$), 
then there is no problem since the demanded availability is still satisfied. 
However, if any $R_{dk}$ falls below 1, then the corresponding SLA will be violated. 
For simplicity, here we assume a simple pricing and refunding model, 
where the charge for serving a user demand $d$ is $g_d$, and if the SLA is violated, 
a fraction $\mu_d$ of $g_d$ will be refunded. 
We use $r_d$ denote the profit of demand $d$ with refunding, such that

@@

\begin{equation}
r_d=
\begin{cases}
g_d &\text{$\forall k \in K: R_{dk} \ge 1$ }\\
(1-\mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation}

@@

\begin{equation}
\label{A-SSS2}
\begin{cases}
y_d \in \{0,1\} &{\forall d \in \hat{D}} \\
r_d  =  g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big) &{\forall d \in \hat{D}} \\
R_{dk} <  M\times y_d+1-y_d &{\forall d \in \hat{D},  k\in K} \\
R_{dk} \ge   y_d &{\forall d \in \hat{D},  k\in K}
\end{cases}
\end{equation}

where $M$ is a constant large enough (e.g., at least larger than the upper bound of $R_{dk}$).

@@

This mixed-integer linear programming  (MILP) problem can be proved to be NP-hard, 
and the proof details can be found in Appendix \ref{appendix1}.
To efficiently solve this problem, we further propose a 2-approximation greedy algorithm.
The key idea is to prioritize demands by the ratio of profit to the allocated bandwidth in a non-decreasing order.
Due to space limitations, the detailed algorithm, as well as the proof on its optimality, 
are put into Appendix \ref{B}.

@@

\subsubsection{A private cloud example}\label{testbedresults}

>>>>

For a specific network scenario $ \mathbf{z}$ (where one link failure occurs) in consideration, 
%let
%$f^{\mathbf{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \mathbf{z}}_k$, where 
%$T^ { \mathbf{z}}_k$ denote the set of surviving tunnels for the s-d pair $k$ under scenario $ \mathbf{z}$.
the ratio of allocated bandwidth to a user's demanded bandwidth is \footnote{This is the same as equation (3), but we omit the superscript $\mathbf{z}$ of $R_{dk}^\mathbf{z}$.}

@@

If for every $k$, $R_{dk}$ is larger than its demand (i.e., $R_{dk} \ge 1$), 
then there is no problem since the demanded availability is still satisfied. 
However, if any $R_{dk}$ falls below 1, then the corresponding SLA will be violated. 
For simplicity, here we assume a simple pricing and refunding model, 
where the charge for serving a user demand $d$ is $g_d$, and if the SLA is violated, 
a fraction $\mu_d$ of $g_d$ will be refunded. 
We use $r_d$ to denote the profit of demand $d$ with refunding, such that

@@

\begin{equation}
r_d=
\begin{cases}
g_d &\text{if $R_{dk} \ge 1$ for every $k \in K$}\\
(1-\mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation}

@@

\begin{equation}
\label{A-SSS2}
\begin{cases}
y_d \in \{0,1\} &{\forall d \in \hat{D}} \\
r_d  =  g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big) &{\forall d \in \hat{D}} \\
R_{dk} <  M\times y_d+1-y_d &{\forall d \in \hat{D},  k\in K} \\
R_{dk} \ge   y_d &{\forall d \in \hat{D},  k\in K}
\end{cases}
\end{equation}
where $M$ is a constant large enough (e.g., at least larger than the upper bound of $R_{dk}$).

@@

The above mixed-integer linear programming  (MILP) problem can be proved to be NP-hard, 
and the proof details can be found in Appendix \ref{appendix1}.
To efficiently solve this problem, we further propose a 2-approximation greedy algorithm.
The key idea is to prioritize demands by the ratio of profit to the allocated bandwidth in a non-decreasing order.
Due to space limitations, the detailed algorithm, as well as the proof on its optimality, 
are put into Appendix \ref{B}.

@@

\textbf{A private cloud example}
